---
title: "Analysis"
author: "Hillebrand"
date: "6 1 2021"
output: html_document
---

```{r setup, include=FALSE, message=FALSE, echo=FALSE}
setwd("~scripts/")
source(~R/phytosize/scripts/phytosize_main.R)
```

## Introduction

Phytoplankton cell size is an important trait, often used as amaster trait to understand resource uptake, edibility, and mobility. (Litchman, Edwards, m.o.)

Cell size has been shown to respond to global change drivers such as nutrients, temperature and grazer presence. Experiments showed size reduction with warming (Sommer, Daufresne). 

Also in large scale spatial trends (Acevedo, Agostino)

But what about temporal trends on ecological time scales

Here we use a monotoring data set

Our hypotheses are

H1 Cell size changes over time within species

H2 Community-weighted mean cell size changes as well

H3 The variance in CWM cell size changes

## Methods

#Sampling and microscopy

#Biovolume

#Statistical analyses
Before analyzing 

For H1, the model was a mixed-effect linear model

year as a fixed factor

Julian day was used as a split variable, increasing until the mid of the year and then decreasing again. Thereby, summer sampling was characterized by high numbers, winter sampling (both at year's beginning and end) by low numbers.

taxonomy as a nested random effect
(phylum/class/order/genus/species)

Station ID as a random factor

In order to compare slopes we analyzed the slope per species using ordinary linear regression of cell size over time, using the slope as 
Perhaps here running a model with random slopes?



###Results

Cell size varies over orders of magnitudes (Fig. 1A)

Still there is a significant reduction in cell size over time (Fig. 1B)

This effect was observed in MLM across all measurements (Fig. 1B)

```{r, echo=FALSE, message=FALSE}

tab1
```

### Plots



```{r, echo=FALSE, message=FALSE}
violin.raw
mod.fig2
```

Fig.1: A: Distribution of cell size per year as violin plot, red dots representing  medians. B: predicted fixed effect  



```{r, echo=FALSE, message=FALSE}
spec.slope
domspec
```

Fig.2: A: Slopes of linear regressions between cell size and time for all species B: raw data for 12 most important species
